\chapter{Third-Party Code and Libraries}

ACOPY - Used to carry out ACO. Version 0.7.0 was used. The library is open source and can be installed via pip.

ACO\_multithreading - Used to carry out ACO but is implemented in a multithreaded way which should speed it up. The latest version on GitHub was used\cite{multithreaded_aco}. This was written for Python 2 so I had to update parts of it to work with Python 3. 

Numpy - Used to store data in numpy multi dimensional arrays for SciKit-Learn and for their distance measures. Version 1.18.1 was used. The library is open source and can be installed via pip.

Scikit-Learn - Used for its clustering algorithms. Open source and version 0.22.1 was used and is available via pip.

Imageio - used to create the incrementally improving images. This library allows you to load in images and turn them into a video. Version 2.8.0 was used and is open source. Can be installed via pip.

ffmpeg - Dependency of ImageIO used to encode video, this is a poython wrapper of the ffmpeg library. Version 1.4 was used. Not sure if this library was actually used or imageio-ffmpeg is used. Available via pip.

imageio-ffmpeg - ffmpeg for imageIO, Version 0.4.1 was used. Availble via pip

matplotlib - Used for all of the graph plotting. Version 3.1.3 was used and is open source. Can be installed via pip.

NetworkX - A graph library ACOPY needs its data to be in this format. Version 2.4 was used. Is available via pip and is open source.

tsplib95 - Library to load in TSPLIB file. Version 0.6.1 was used and is available to install via pip. Is open source.
